My title

### 2024-03-16 paper/paper.qmd
Edits

saveRDS(
  political_preferences,
  file = "models/political_preference.rds"
)
```

@@

Define $y_i$ as the ... Then $\beta_i$ is the ... and $\gamma_i$ is the ...

@@

```{r}
#| echo: false
#| warning: false
#| message: false
political_preferences <-
  readRDS(file = "models/political_preferences.rds")
```

>>>>

saveRDS(
  political_preferences,
  file = "models/political_preference.rds"
)

```

@@

Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\beta_i$ is the ... and $\gamma_i$ is the ...

@@

```{r}
#| echo: false
#| warning: false
#| message: false
political_preferences <-
  readRDS(file = "models/political_preference.rds")
```
